Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-07-24 latex/discussion.tex
Intro finished, looking for fig and caption of eigenvectors

\section{Answers to questions posed in the introduction}
First of all, it is important to state that we do not view measurement
clusterization as undesirable, nor do we believe it should be avoided
at all. Clusterization is a peculiar phenomenon and it is perfectly
reasonable for someone to argue against the D-optimality criterion
based on the fact that it results in clustered designs. We have seen,
however that there is perfectly reasonable explanation for
clusterization, i.e.~that clusterization arises when we seek a
designWe have shown that clusterization is an innevitable conseqeunce
of having a problem with modes of higher uncertainty than
others. Clusterization manifests the true underlying objective

>>>>

\section{Answers to questions posed in the introduction}

### 2024-07-24 latex/intro.tex
Intro finished, looking for fig and caption of eigenvectors

\subsection{A toy model: the 1D heat equation}
For concreteness, let us now consider a toy model of a physical process
for which we wish to solve an inverse problem: a partial differential
equation known as the \emph{heat equation} in one dimension (1D heat
equation henceforth, see details below). Readers less familiar with
partial differential equations can think of the following setup:
before us there is a perfectly insulated metal rod. At each point on
the rod the temperature is different and unknown, and we call this
temperature distribution the \emph{initial condition}. We wait for a
short time $T$ and let the heat dissipate a bit inside the rod. The
heat equation determines the heat distribution inside the rod at time
$t=T$.

@@

@@

\subsection{Measurement Clusterization}
Surprisingly, A- and D-optimal designs for inverse problems have been
observed to yield remarkably similar measurements in certain cases
\cite{fedorov1996, nyberg2012, fedorov1997, Ucinski05,
  neitzel2019sparse}. This phenomenon is illustrated for our toy
inverse problem in Fig.~\ref{fig:clusterization illustration}, where
D-optimal measurement locations are shown for different numbers of
measurements. Notably, for six measurements, a D-optimal design yields
two sets of measurements that are almost indistinguishable from one
another. We refer to this intriguing phenomenon as \emph{measurement
clusterization} \cite{Ucinski05}. We consider a design to be
\emph{clustered} when two or more of its constituent measurements are
identical.

@@

Clusterization should not be confused with either repetition nor with
replication, which are commonly viewed as beneficial and even
necessary aspects of an optimal design \cite{morris, fisher
  schafer2001replication}. For example, in his famous milk and tea
experiment, \cite[Section 11]{fisher} suggested that repetition is a
"way of enlarging the experiment and, thereby, increasing its
sensitiveness". In another example, \cite{fay2000rainfall} measured
the effect of rainfall on grass growth in plots of land. The
experiment involved fifteen "rainfall manipulation shelters", where
"Four rainfall manipulation treatments (three replicates) then were
assigned to 12 of the plots". It seems reasonable the researchers
replicate the phenomenon they are trying to study. Clusterization is
different: a clustered design in the rainfall experiment would imply
the researchers should take a repeated measurement \emph{on the same
plot}, at the expense of measuring grass growth in other plots. In
sharp contrast to repetition and replication, clusterization is highly
nonintuitive and, as we will see, its origins run considerably deeper.

Researchers of inverse problems widely agree that measurement
clusterization is undesirable \cite{fedorov1996, nyberg2012,
  fedorov1997, Ucinski05, neitzel2019sparse}, prompting the
exploration of various remedies to address this issue. One approach
involves merging close measurements \cite{fedorov1997}; however, this
strategy merely overlooks the phenomenon of measurement
clusterization. An alternative solution lies in
\emph{clusterization-free design}s, where measurement locations are
deliberately chosen to be distant from one another. This can be
achieved by imposing distance constraints between measurements or by
introducing correlated errors that account for both observation error
and model misspecification \cite{Ucinski05}. For instance, in the
context of time-series analysis for pharmacokinetic experiments,
measurement clusterization can be mitigated by incorporating the
modeling of auto-correlation time within the noise terms
\cite{nyberg2012}.

@@

Avoiding measurement clusterization is a pragmatic approach:
intuitively, researchers recognize that measurement clusterization is
undesirable, even though the underlying reasons may not be fully
clear. Consequently, they strive to prevent it and devise various
methodologies to avoid measurement clusterization. Yet each and every
one of these methodologies achieves its objective by imposing
restrictions on measurement locations, thereby fundamentally altering
the optimal design problem. To the best of my knowledge, no previous
study has tried to address some seemingly simple yet fundamental
questions:
%
Why does imposing correlations between observations alleviate
measurement clusterization?
%
Is measurement clusterization a generic phenomenon? 
%
And, most importantly: Why does measurement clusterization occur?
%
%Should we aim to avoid measurement clusterization?
%
%Is it possible to substitute an optimal clustered design with an
%equally optimal non-clustered design?
%Can an optimal clustered design be relpaced with an equally optimal
%non-clustered design?

\subsection{Contribution}
The primary objective of this study is to provide a deep understanding
of measurement clusterization by addressing the aforementioned
questions. Our focus centers around investigating the Bayesian
D-optimality criterion. We conduct an analysis of Bayesian D-optimal
designs within the context of linear inverse problems over Hilbert
spaces. We propose a novel relaxed model for D-optimality that
maintains analytical tractability and enables the identification of
D-optimal designs using Lagrange multipliers. This analytical
framework facilitates the exploration of the questions posed at the
end of the previous paragraph:

\begin{enumerate}
\item \label{q:generic} \textbf{Is measurement clusterization a
  generic phenomenon?}
  %\subsection{An answer for Question \ref{q:generic}: Genericity of measurement clusterization}
  %% Computer implementation of Lemma \ref{thm:char} for the inverse
  %% problem outlined in Section \ref{section:how} also generates \(\obs\)
  %% as a solution to the D-optimal design problem.  Furthermore,
  We give two complementing answers to this question. First, from a
  theoretical perspective, we show that clusterization barely depends
  on the specifics of the prior, so long as it is Gaussian. We show
  that the structure of the decay of the eigenvalues of the
  pushforward prior covariance determine clusterization. The decay of
  these eigenvalues depends on how ill-posed the problem at hand is
  and does not depend much on the prior. see Theorem \ref{thm:char}
  and the Discussion for details. From a numerical experiments
  perspective, simulations of our model give rise to D-optimal designs
  that exhibit clusterization more than 95\% of the time (see Section
  \ref{subsec:lemma sims} for details). Given the genericity of our
  model, we expect measurement clusterization to be a generic and
  ubiquitous phenomenon.

\item \label{q:mitigate} \textbf{Why does imposing correlations
  between observations alleviate measurement clusterization?} In
  Section \ref{section:non vanishing}, we rigorously demonstrate the
  role of model error in mitigating clusterization, thereby
  corroborating earlier observations made by various researchers. We
  also show that adding to the inverse problem of the 1D heat
  equationan error term corresponding to correlations between
  measurements mitigates clusterization, see Section \ref{subsec:corr
    errors sims}.

\item \label{q:why} \textbf{Why does measurement clusterization
  occur?} Answering this question is the main contribution of this
  study, and it is arrived at in Section \ref{section:why}. There, we
  present a compelling explanation for the optimality of clustered
  designs in the absence of model error. Our analysis reveals that a
  D-optimal design focuses on a select set of prior eigenvectors,
  specifically those with the largest eigenvalues in the prior
  covariance spectrum. In practical scenarios, the number of locations
  where (a) the relevant prior eigenvectors are significantly large,
  and (b) other eigenvectors are close to zero, is
  limited. Consequently, the clusterization of measurements arises as
  a natural consequence of the pigeonhole principle, as there are more
  measurements available than there are locations satisfying
  conditions (a) and (b). See Fig~\ref{fig:why}.

@@

%% \item \label{q:replace} \textbf{Is it possible to substitute an
%%   optimal clustered design with an equally optimal non-clustered
%%   design?} In Section \ref{section:vanishing}, we answer this question
%%   in the affirmative, although we show that numerical experiments
%%   conducted using our model indicate a strong preference for clustered
%%   designs.

\end{enumerate}

Our results have several implications. Our answer to Question
\ref{q:generic} implies that encountering clusterization should be
expected in many different problems across many different scientific
fields. Thus, researchers that encounter clusterization should not be
surprised or wary. In Our answer to Question \ref{q:why}, we explain
what is the cause of clusterization. As it appears, the cause is
generic: a D-optimal design reduces uncertainty for a select set of
prior covariance eigenvectors --- those with the most prior
uncertainty, i.e.~those the practitioner cares about the most!
Consequently, practitioners should not try to avoid measurement
clusterization. Rather, practitioners should take repeated
measurements (e.g.~in MRI and borehole tomography), increase apparatus
sensitivity (e.g.~in EIT), or take consecutive measurements (e.g.~in
the 1D heat equation). Overall, we show that measurement
clusterization is a natural and (almost) inevitable part of Bayesian
D-optimal designs.

\subsubsection{Further Contributions}
In Theorem \ref{thm:char}, we also show that D-optimal designs are
best understood in the sapce of \emph{observations}, see Section
\ref{section:vanishing} for a precise statement. This is in accordance
with previous work by \cite{koval2020}, who showed that A-optimal
designs are best constructed in the space of observations.

In the process of proving Theorem \ref{thm:char} we prove and
generalize several lemmas. Among those, is Lemma \ref{lemma:free},
which is a lemma in linear algebra that (to the the best of my
knowledge) is novel: We decompose a symmetric positive definite matrix
\(M \in \mathbb{R}^{k \times k}\) with \(\ttr M = m \in \mathbb{N}\)
as \(M = AA^t\), where \(A\in \mathbb{R}^{k \times m}\) has unit norm
columns.

>>>>

\subsection{A toy model: the 1D heat equation}\label{subsec:toy}
For concreteness, let us now consider a toy model of a physical process
for which we wish to solve an inverse problem: a partial differential
equation known as the \emph{heat equation} in one dimension (1D heat
equation henceforth, see details below). Readers less familiar with
partial differential equations can think of the following setup:
before us there is a perfectly insulated metal rod. At each point on
the rod the temperature is different and unknown, and we call this
temperature distribution the \emph{initial condition}. We wait for a
short time $T$ and let the heat dissipate a bit inside the rod. The
heat equation determines the heat distribution inside the rod at time
$t=T$.

@@

Solving the 1D heat equation is straightforward. Any initial heat
distribution $u_0\in L^2(\Omega)$ that satisfies the homogeneous
Dirichlet boundary condition is a linear combination of sines
$\ev_n(x) = \sin(2\pi n x)$. Now, note that $\ev_n$ are in fact
eigenvectors of the Laplace operator: $\Delta \ev_n = -(2\pi
n)^2\ev_n$. The linearity of the heat equation allows us to solve in
Fourier / frequency space. It is important to note that when solving
the heat equation we \emph{invert} the Laplace
operator. I.e.~eigenvalues of the linear operator associated with the
heat equation are $(2\pi n)^{-2}$.

@@

\subsection{Measurement Clusterization}
Surprisingly, A- and D-optimal designs for inverse problems have been
observed to yield remarkably similar measurements in certain cases
\cite{fedorov1996, nyberg2012, fedorov1997, Ucinski05,
  neitzel2019sparse}. This phenomenon is illustrated for our toy
inverse problem in Fig.~\ref{fig:clusterization illustration}, where
D-optimal measurement locations are shown for different numbers of
measurements. Notably, for six measurements, a D-optimal design yields
two sets of measurements that are identical. We refer to this
intriguing phenomenon as \emph{measurement clusterization}
\cite{Ucinski05}. We consider a design to be \emph{clustered} when two
or more of its constituent measurements are identical.

@@

Clusterization should not be confused with either repetition nor with
replication, which are commonly viewed as beneficial and even
necessary aspects of an optimal design \cite{morris, fisher
  schafer2001replication}. For example, in his famous milk and tea
experiment, \cite[Section 11]{fisher} suggested that repetition is a
"way of enlarging the experiment and, thereby, increasing its
sensitiveness". In another example, \cite{fay2000rainfall} measured
the effect of rainfall on grass growth in plots of land. The
experiment involved fifteen "rainfall manipulation shelters", where
"Four rainfall manipulation treatments (three replicates) then were
assigned to 12 of the plots". It seems reasonable the researchers
replicate the phenomenon they are trying to study. Clusterization is
different: a clustered design in the rainfall experiment would imply
the researchers should take a repeated measurement \emph{on the same
plot}, at the expense of measuring grass growth in other plots. In
sharp contrast to repetition and replication, clusterization is highly
nonintuitive and we will see that its origins run considerably deeper.

Researchers of inverse problems widely agree that measurement
clusterization is undesirable
\cite{fedorovDesignSpatialExperiments1996, nyberg2012, fedorov1997,
  Ucinski05, neitzel2019sparse}, prompting the exploration of various
remedies to address this issue. One approach involves merging close
measurements \cite{fedorov1997}; however, this strategy merely
overlooks the phenomenon of measurement clusterization. An alternative
solution lies in \emph{clusterization-free design}s, where measurement
locations are deliberately chosen to be distant from one another. This
can be achieved by imposing distance constraints between measurements
or by introducing correlated errors that account for both observation
error and model misspecification \cite{Ucinski05}. For instance, in
the context of time-series analysis for pharmacokinetic experiments,
measurement clusterization can be mitigated by incorporating the
modeling of auto-correlation time within the noise terms
\cite{nyberg2012}.

@@

Avoiding measurement clusterization is a pragmatic approach:
intuitively, researchers recognize that measurement clusterization is
undesirable, even though the underlying reasons may not be fully
clear. Consequently, they strive to prevent it and devise various
methodologies to avoid it. Yet each and every one of these
methodologies achieves its objective by imposing restrictions on
measurement locations, thereby fundamentally altering the optimal
design problem. To the best of my knowledge, no previous study has
tried to address some seemingly simple yet fundamental questions:
%
Why does imposing correlations between observations alleviate
measurement clusterization?
%
Is measurement clusterization a generic phenomenon? 
%
And, most importantly: Why does measurement clusterization occur?
%
%Should we aim to avoid measurement clusterization?
%
%Is it possible to substitute an optimal clustered design with an
%equally optimal non-clustered design?
%Can an optimal clustered design be relpaced with an equally optimal
%non-clustered design?

\subsection{Contribution}
The primary objective of this study is to provide a deep understanding
of measurement clusterization by addressing the aforementioned
questions. Our focus centers around investigating the Bayesian
D-optimality criterion. We conduct an analysis of Bayesian D-optimal
designs within the context of linear inverse problems over Hilbert
spaces and study two inverse problems: (a) In Sections
\ref{section:prelim} and \ref{section:D and grad} we propose a novel
relaxed model for an inverse problem where D-optimality maintains
analytical tractability. In this model D-optimal designs are
identified via Lagrange multipliers. This analytical framework
facilitates the exploration of the questions posed at the end of the
previous paragraph. (b) we also study the inverse problem of the 1D
heat equation (see Section \ref{subsec:toy} above). Investigating both
inverse problems allows us to answer the questions posed in the
previous section:

\begin{enumerate}
\item \label{q:generic} \textbf{Is measurement clusterization a
  generic phenomenon?}
  %\subsection{An answer for Question \ref{q:generic}: Genericity of measurement clusterization}
  %% Computer implementation of Lemma \ref{thm:char} for the inverse
  %% problem outlined in Section \ref{section:how} also generates \(\obs\)
  %% as a solution to the D-optimal design problem.  Furthermore,
  We give two complementing answers to this question. First, from a
  theoretical perspective, we show that clusterization barely depends
  on the specifics of the prior, so long as it is Gaussian. We show
  that the structure of the decay of the eigenvalues of the
  pushforward prior covariance determine clusterization. The decay of
  these eigenvalues depends mostly on how ill-posed the problem at
  hand is and does not depend much on the prior. See Section
  \ref{section:vanishing} --- particularly, Theorem \ref{thm:char} and
  the discussion following it. We also show results of numerical
  experiments, where simulations of our model give rise to D-optimal
  designs that exhibit clusterization with very high probability in
  Section \ref{subsec:lemma sims}. Thus, given the genericity of our
  model, we expect measurement clusterization to be a generic and
  ubiquitous phenomenon.

\item \label{q:mitigate} \textbf{Why does imposing correlations
  between observations alleviate measurement clusterization?} In
  Section \ref{section:non vanishing}, we rigorously demonstrate the
  role of model error in mitigating clusterization, thereby
  corroborating earlier observations made by various
  researchers. Specifically, our proof shows that identical
  measurements result in no gain in design criterion in when
  observation error tends to zero. Moreover, in Section
  \ref{subsec:corr errors sims}, we show that adding to the inverse
  problem of the 1D heat equation an error term corresponding to
  correlations between measurements mitigates clusterization.

\item \label{q:why} \textbf{Why does measurement clusterization
  occur?} In Section \ref{subsec:why} we give a compelling answer to
  this question by transporting insights we gain from our analytically
  tractable relaxed model to the inverse problem of the 1D heat
  equation. Our analysis reveals that a D-optimal design focuses on a
  select set of prior eigenvectors, specifically those with the
  largest eigenvalues in the prior covariance spectrum. In practical
  scenarios, the number of locations where (a) all relevant prior
  eigenvectors are significantly large, and (b) other eigenvectors are
  close to zero, is limited. Consequently, the clusterization of
  measurements arises as a natural consequence of the pigeonhole
  principle, as there are more measurements available than there are
  locations satisfying conditions (a) and (b). See Fig~\ref{fig:why}.

@@

%% \item \label{q:replace} \textbf{Is it possible to substitute an
%%   optimal clustered design with an equally optimal non-clustered
%%   design?} In Section \ref{section:vanishing}, we answer this question
%%   in the affirmative, although we show that numerical experiments
%%   conducted using our model indicate a strong preference for clustered
%%   designs.
\end{enumerate}

\subsubsection{Implications}
Our answer to Question \ref{q:generic} implies that encountering
clusterization should be expected in many different problems across
many different scientific fields. Thus, researchers that encounter
clusterization should not be surprised or wary. In Our answer to
Question \ref{q:why}, we explain what our view of the cause of
clusterization. As it appears, the cause is generic (see Question
\ref{q:why} above): a D-optimal design reduces uncertainty for a
select set of prior covariance eigenvectors --- those with the most
prior uncertainty, i.e.~those the practitioner cares about the most!
Consequently, practitioners should not try to avoid measurement
clusterization. Rather, practitioners should take repeated
measurements (e.g.~in MRI and borehole tomography), increase apparatus
sensitivity (e.g.~in EIT), or take consecutive measurements (e.g.~in
the 1D heat equation). Overall, we show that measurement
clusterization is a natural and (almost) inevitable part of Bayesian
D-optimal designs.

One interesting implication of the analysis presented here is that
clusterization can be expected once the number of measurements exceeds
the number of relevant eigenvectors. Since leading eigenvectors
typically correspond to slow variations in space and/or time,
clusterization could be used to estimate the number of relevant
degrees of freedom, and even to reduce the complexity of a
computational model, e.g.~by dropping discretization points.

It is important to note that we do not view measurement clusterization
as undesirable, nor do we believe it should be avoided at
all. Clusterization is a peculiar phenomenon and it is perfectly
reasonable for someone to argue against the D-optimality criterion
based on the fact that it results in clustered designs. We have seen,
however that there is perfectly reasonable explanation for
clusterization, i.e.~that clusterization arises when we seek a
designWe have shown that clusterization is an innevitable conseqeunce
of having a problem with modes of higher uncertainty than
others. Clusterization manifests the true underlying objective

\subsubsection{Other Contributions}
In Theorem \ref{thm:char}, we also show that D-optimal designs are
best understood in the sapce of \emph{observations}, see Section
\ref{section:vanishing} for a precise statement. This is in accordance
with previous work by \cite{koval2020}, who showed that A-optimal
designs are best constructed in the space of observations.

In the process of proving Theorem \ref{thm:char} we prove and
generalize several lemmas. Among those, is Lemma \ref{lemma:free},
which is (to the the best of my knowledge) novel: We decompose a
symmetric positive definite matrix \(M \in \mathbb{R}^{k \times k}\)
with \(\ttr M = m \in \mathbb{N}\) as \(M = AA^t\), where \(A\in
\mathbb{R}^{k \times m}\) has unit norm columns.

### 2024-07-24 latex/numerix.tex
before diff
Fixed intro and prelims
Intro finished, looking for fig and caption of eigenvectors

\section{Numerical Experiments}
We provide numerical evidence supporting our conclusions.

\subsection{Simulating Lemma \ref{lemma:free}}\label{subsec:lemma sims}
Lemma \ref{lemma:free} is used to construct D-optimal designs as a
part of the proof of Theorem \ref{thm:char}. We implement the
construction in Lemma \ref{lemma:free} (see module \texttt{zeros.py}
in the accompanying
\href{https://github.com/yairdaon/OED}{repository}). We iterate over
the number of measurements $m \in \{4,\dots, 15\}$, and for every $m$
we then iterate over $k:=\rank \obs^*\obs \in \{2,\dots, m-1\}$. For
each pair $m,k$ we run $N=50000$ simulations according to the
following steps:
\begin{enumerate}
\item Generate random diagonal $D\in \mathbb{R}^{k\times k}$ and
  normalize it so that $\ttr D = m$.
\item Conjugate $D$ by a random orthogonal matrix to form a positive
  semi-definite $M := UDU^t \in \mathbb{R}^{k\times k}$.
\item Apply the construction of Lemma \ref{lemma:free} to calculate
  $A$ such that $AA^t = M$, where $A$ has unit norm columns.
\item We call $A$ "clustered" if $A$ has two or more identical columns
  (up to some numerical precision threshold).
\end{enumerate}
We then calculate the fraction of clustered designs of the $N=5000$
simulations we ran, for each pair $m,k$. Full results in the
\texttt{simulations.csv} file within the accompanying
\href{https://github.com/yairdaon/OED}{repository}), below we give a
brief description of the results.

Clusteriztion occured at high rates ($>95\%$) whenever $m-k > 1$; see
Fig.~\ref{fig:sim AAt}. Hence, in these simulations, clusterization is
a generic property. However, when $m-k \leq 2$, clusterization does
not occur. We do not why and further investigation into this
phenomenon is out of scope for the current study.

@@

\subsection{Correlated errors}\label{subsec:corr errors sims}
In order to verify the results of Section \ref{section:non vanishing},
we run simulations of the inverse problem of the 1D heat equation
\ref{subsec:1d heat} with nonvanishing model error. We take a model
correlation of \(\modcov = \prcov^2 \). Indeed, adding model
correlation pushes measurements apart as can be seen in
Fig.~\ref{fig:corr errors}. Code generating the image below can be
located at module \texttt{clusterization.py} in the accompanying
\href{https://github.com/yairdaon/OED}{repository}).

\begin{figure}
    \centering
    \includegraphics[height=0.5\textwidth]{dst_modelError4.pdf}
    \caption{Model correlation mitigates clusterization. We add a
      model correlation term to the error terms in the 1D heat
      equation inverse problem. Lo and behold, measurements are not
      close anymore and are pushed away thanks to the model error
      term.}
  \label{fig:corr errors}
\end{figure}

>>>>

\section{Numerical Experiments}
%We provide numerical evidence supporting our conclusions.

\subsection{Simulating Lemma \ref{lemma:free}}\label{subsec:lemma sims}
In the proof of Theorem \ref{thm:char} we utilize Lemma
\ref{lemma:free} to construct D-optimal designs. We implement the
construction in Lemma \ref{lemma:free} with the goal of testing
numerically how prevalent are clustered designs. We iterate over the
number of measurements $m \in \{4,\dots, 15\}$, and for every $m$ we
then iterate over $k:=\rank \obs^*\obs \in \{2,\dots, m-1\}$. For each
pair $m,k$ we run $N=5000$ simulations according to the following
steps:
\begin{enumerate}
\item Generate random diagonal $D\in \mathbb{R}^{k\times k}$ with
  entries $\log (d_i) \sim \mathcal{N}(5,1)$ and normalize it so that
  $\ttr D = m$.
\item Conjugate $D$ by a random orthogonal matrix to form a positive
  semi-definite $M := UDU^t \in \mathbb{R}^{k\times k}$.
\item Apply the construction of Lemma \ref{lemma:free} to calculate
  $A$ such that $AA^t = M$, where $A$ has unit norm columns.
\item Since columns of $A$ correspond to measurement vectors, we call
  $A$ "clustered" if $A$ has two or more identical columns (up to some
  numerical precision threshold).
\end{enumerate}
We then calculate the fraction of clustered designs of the simulations
we ran, for each pair $m,k$. Clusteriztion occured at high rates
($>95\%$) whenever $m-k > 1$; see Fig.~\ref{fig:sim AAt}. Hence, in
these simulations, clusterization is a generic property. However, when
$m-k \leq 2$, clusterization does not occur. We do not why and further
investigation into this phenomenon is out of scope for the current
study.

@@

Full results are located in the \texttt{simulations.csv} file within
the accompanying \href{https://github.com/yairdaon/OED}{repository},
code implementing our experiments is located in module
\texttt{zeros.py} of said repository.

\subsection{Correlated errors}\label{subsec:corr errors sims}
In order to verify the results of Section \ref{section:non vanishing},
we run simulations of the inverse problem of the 1D heat equation with
nonvanishing model error \(\modcov = \prcov^2 \). Indeed, including model
correlation pushes measurements apart, see Fig.~\ref{fig:corr
  errors}. Code generating the image below is located in module
\texttt{clusterization.py} in the accompanying
\href{https://github.com/yairdaon/OED}{repository}.

\begin{figure}
    \centering
    \includegraphics[height=0.5\textwidth]{dst_modelError4.png}
    \caption{Model correlation mitigates clusterization. We add a
      model correlation term to the error terms in the 1D heat
      equation inverse problem. Lo and behold, measurements are not
      close anymore and are pushed away thanks to the model error
      term.}
  \label{fig:corr errors}
\end{figure}

### 2024-07-24 latex/prelims.tex
Intro finished, looking for fig and caption of eigenvectors

\subsection{Bayesian D-Optimal Designs}\label{subsec:D optimal design} 
A Bayesian D-optimal design maximizes the expected Kullback-Leibler
(KL) divergence between posterior \(\post\) and prior measures
\(\pr\). For arbitrary posterior and prior measures, the KL divergence
is defined, analogously to eq.~\ref{eq:basic KL}, via the
Radon-Nikodym derivative:
\begin{equation*}
  D_{KL}(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(\param) \der \post(\param).
\end{equation*}

>>>>

\subsection{Bayesian D-Optimal Designs}\label{subsec:D optimal design} 
A Bayesian D-optimal design maximizes the expected KL divergence
between posterior \(\post\) and prior measures \(\pr\). For arbitrary
posterior and prior measures, the KL divergence is defined,
analogously to eq.~\ref{eq:basic KL}, via the Radon-Nikodym
derivative:
\begin{equation*}
  D_{KL}(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(\param) \der \post(\param).
\end{equation*}

### 2024-07-24 latex/refs.tex
Intro finished, looking for fig and caption of eigenvectors

While the results in the paper provide some novel insights on the
topic, I believe the current version of the manuscript is far from the
standard required by Bayesian Analysis. Let me raise immediately my
main concern: on p.4 the author describes the generality of
measurements clus- terisation as the first main question being
explored, which is answered via, quoting, "randomized numerical
simulations that exhibit clusterization more than 95\% of the time
(see the code in sup- plementary material)". However, in the version
of the supplementary materials I had access to there is no further
mention of these numerical simulations and results; only a link to a
Github repository is provided, which is however not
functioning. Evidently, this issue needs to be fixed before any future
consideration can be given to the manuscript. For example, a detailed
description of the repeated experiments could be provided either in
the main article or in the supplement, with ta- bles indicating the
various values of the parameters for the simulations and the precise
percentages obtained. Also, the code needs to be publicly available
for reproducibility.

>>>>

While the results in the paper provide some novel insights on the
topic, I believe the current version of the manuscript is far from the
standard required by Bayesian Analysis. Let me raise immediately my
main concern: on p.4 the author describes the generality of
measurements clusterisation as the first main question being explored,
which is answered via, quoting, "randomized numerical simulations that
exhibit clusterization more than 95\% of the time (see the code in
supplementary material)". However, in the version of the supplementary
materials I had access to there is no further mention of these
numerical simulations and results; only a link to a Github repository
is provided, which is however not functioning. Evidently, this issue
needs to be fixed before any future consideration can be given to the
manuscript. For example, a detailed description of the repeated
experiments could be provided either in the main article or in the
supplement, with tables indicating the various values of the
parameters for the simulations and the precise percentages
obtained. Also, the code needs to be publicly available for
reproducibility.
